Appendix

### 2018-07-03 manuscript/appendix.Rmd
add nla comparison

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

@@

```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3}
plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
          title = "Link Length")
```

```{r partition_example_scatter, fig.height=2, fig.width=2.2}
results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

@@

```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE}
plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
          title = "Link Length")
```

```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE}
results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits

@@

```{r nes_vs_nla, message=FALSE, warning=FALSE}
nla <- nla_load(2012)

tp <- select(nla$waterchem_wide, PTL_RESULT, UID) %>%
      left_join(select(nla$wide_siteinfo, AREA_HA, SITE_ID, UID)) %>%
      group_by(SITE_ID) %>%
      summarize(tp = median(PTL_RESULT), area = median(AREA_HA) / 100)

chl  <- select(nla$chla_wide, CHLX_RESULT, UID)  %>%
        left_join(select(nla$wide_siteinfo, SITE_ID, UID)) %>%
        group_by(SITE_ID) %>%
        summarize(chl = median(CHLX_RESULT))

secchi  <- select(nla$secchi, SECCHI, SITE_ID)  %>%
           group_by(SITE_ID) %>%
           summarize(secchi = median(SECCHI))

depth <- select(nla$wide_phab, DEPTH_AT_STATION, SITE_ID)  %>%
           group_by(SITE_ID) %>%
           summarize(depth = median(DEPTH_AT_STATION))

nla <- reduce(list(tp, chl, secchi, depth), left_join)
# skimr::skim(res)
nla <- gather(select(nla, -SITE_ID), variable, value)
nla$id <- "nla"

nes <- select(nes_iws, tp, area = surface_area, chl, secchi, depth = maxdepth)
nes$tp <- 1000 * nes$tp # mg to ug
nes <- gather(nes, variable, value)
nes$id <- "nes"

res <- rbind(nla, nes)

# ggplot(data = dplyr::filter(res, variable == "chl"), aes(y = id, x = value + 0.1)) + 
#   geom_density_ridges() + 
#   scale_x_log10()

ggplot(data = res, aes(y = id, x = value + 0.1)) + 
  geom_density_ridges() + 
  scale_x_log10() + 
  facet_wrap(~variable) + 
  theme(axis.title = element_blank())
```
